Shapes analysis for time series.

### 2024-09-03 NEURIPS24/appendix.tex
Revert "Delete NEURIPS24 directory"
This reverts commit e09ecaea218c43964bb3eb1e2a9a2c5bfd236ded.

\section{Appendix for experiment: Analysis of respiratory behavior in mice}
\subsection{Settings}
\label{appendix: mice_exp_setting}

\section{Appendix for experiment: TS-LDDMM representation identifiability}
In this experiment, we evaluate the ability of TS-LDDMM to retrieve the parameter $v_0^*$ that encodes the deformation $\varphi^{\{v_0^*\}}$ acting on a time series graph $\msg$ by solving the geodesic shooting problem \eqref{eq:relaxation} between $\msg$ and $\varphi^{\{v_0^*\}}.\msg$. Parameter identifiability is an important property for subsequent statistical analysis. Results show that TS-LDDMM representations are identifiable or weakly identifiable depending on the velocity field kernel $K_G$ specification.

@@

\section{Appendix for experiment: Classification benchmark on regularly sampled datasets}

@@

>>>>

\section{Appendix for experiment: TS-LDDMM representation identifiability}
\label{appendix: identifiability}
In this experiment, we evaluate the ability of TS-LDDMM to retrieve the parameter $v_0^*$ that encodes the deformation $\varphi^{\{v_0^*\}}$ acting on a time series graph $\msg$ by solving the geodesic shooting problem \eqref{eq:relaxation} between $\msg$ and $\varphi^{\{v_0^*\}}.\msg$. Parameter identifiability is an important property for subsequent statistical analysis. Results show that TS-LDDMM representations are identifiable or weakly identifiable depending on the velocity field kernel $K_G$ specification.

@@

\section{Appendix for experiment: Classification benchmark on regularly sampled datasets}
\label{appendix: shape_classification}

@@

\section{Appendix for experiment: Analysis of respiratory behavior in mice}
\label{appendix: mice_exp_setting}

\subsection{Settings}

### 2024-09-03 NEURIPS24/experiment.tex
Revert "Delete NEURIPS24 directory"
This reverts commit e09ecaea218c43964bb3eb1e2a9a2c5bfd236ded.

\begin{enumerate}
    \item \textbf{TS-LDDMM representation identifiability, \Cref{appendix: settings_identifiability}:} On synthetic data, we evaluate the ability of our method to retrieve the parameter $v_0^*$ that encodes the deformation $\varphi^{\{v_0^*\}}$ acting on a time series graph $\msg$ by solving the geodesic shooting problem \eqref{eq:relaxation} between $\msg$ and $\varphi^{\{v_0^*\}}.\msg$.
     \textbf{Results} show that TS-LDDMM representations are identifiable or weakly identifiable depending on the velocity field kernel $K_G$ specification.

    \item \textbf{Robustness to irregular sampling, \Cref{appendix: benchmark robustness}:} We compare the robustness of TS-LDDMM representation with 9 URL methods handling irregularly sampled multivariate time series on 15 shape-based datasets (7 univariates \& 8 multivariates).
     We assess methods' classification performances under regular sampling (0\% missing rate) and three irregular sampling regimes (30\%, 50\%, and 70\% missing rates), according to the protocol depicted in \cite{kidger2020neural}.
      \textbf{Results} show that our method, TS-LDDMM, outperforms all methods for sampling regimes with missing rates: 0\%, 30\%, and 50\%.
      %{\color{red} J'enlèverai cette phrase ou je développerai en Appendix : The performance decrease of the Kernel-SVC based on TS-LDDMM representation is sensibly due to the misspecification of its regularization parameter.}

    \item \textbf{Classification benchmark on regularly sampled datasets, \Cref{appendix: settings_classification}:} We compare performances of a kernel support vector machine (SVC) algorithm based on TS-LDDMM representation with 3 state-of-the-art classification methods from shape analysis on 15 shape-based datasets (7 univariates \& 8 multivariates). \textbf{Results} show that the TS-LDDMM-based method outperforms other methods (best performances over 13 datasets), making TS-LDDMM representation relevant for time series shape analysis.
\end{enumerate}
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width = \textwidth]{pictures/ts_ddmm_shooting.pdf}
    \caption{TS-LDDMM}
    \label{fig:ts-lddmm shooting}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width = \textwidth]{pictures/lddmm_shooting.pdf}
    \caption{LDDMM}
    \label{fig:lddmm shooting}
  \end{subfigure}
  \caption{Analysis of the two principal components (PC) related to mice' respiratory cycles before exposure for TS-LDDMM \Cref{fig:ts-lddmm shooting}, and LDDMM \Cref{fig:lddmm shooting}.
  In both cases, I) displays PC densities according to mice genotype and II) displays  deformations of the reference graph $S_0$ along each PC.}
  \label{fig:exp1}
\end{figure*}

>>>>

\begin{enumerate}
    \item \textbf{TS-LDDMM representation identifiability, \Cref{appendix: identifiability}:} On synthetic data, we evaluate the ability of our method to retrieve the parameter $v_0^*$ that encodes the deformation $\varphi^{\{v_0^*\}}$ acting on a time series graph $\msg$ by solving the geodesic shooting problem \eqref{eq:relaxation} between $\msg$ and $\varphi^{\{v_0^*\}}.\msg$.
     \textbf{Results} show that TS-LDDMM representations are identifiable or weakly identifiable depending on the velocity field kernel $K_G$ specification.

    \item \textbf{Robustness to irregular sampling, \Cref{appendix: robustness}:} We compare the robustness of TS-LDDMM representation with 9 URL methods handling irregularly sampled multivariate time series on 15 shape-based datasets (7 univariates \& 8 multivariates).
     We assess methods' classification performances under regular sampling (0\% missing rate) and three irregular sampling regimes (30\%, 50\%, and 70\% missing rates), according to the protocol depicted in \cite{kidger2020neural}.
      \textbf{Results} show that our method, TS-LDDMM, outperforms all methods for sampling regimes with missing rates: 0\%, 30\%, and 50\%.
      %{\color{red} J'enlèverai cette phrase ou je développerai en Appendix : The performance decrease of the Kernel-SVC based on TS-LDDMM representation is sensibly due to the misspecification of its regularization parameter.}

    \item \textbf{Classification benchmark on regularly sampled datasets, \Cref{appendix: shape_classification}:} We compare performances of a kernel support vector machine (SVC) algorithm based on TS-LDDMM representation with 3 state-of-the-art classification methods from shape analysis on 15 shape-based datasets (7 univariates \& 8 multivariates). \textbf{Results} show that the TS-LDDMM-based method outperforms other methods (best performances over 13 datasets), making TS-LDDMM representation relevant for time series shape analysis.
\end{enumerate}
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width = \textwidth]{pictures/ts_ddmm_shooting.pdf}
    \caption{TS-LDDMM}
    \label{fig:ts-lddmm shooting}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width = \textwidth]{pictures/lddmm_shooting.pdf}
    \caption{LDDMM}
    \label{fig:lddmm shooting}
  \end{subfigure}
  \caption{Analysis of the two principal components (PC) related to mice' respiratory cycles before exposure for TS-LDDMM \Cref{fig:ts-lddmm shooting}, and LDDMM \Cref{fig:lddmm shooting}.
  In both cases, I) displays PC densities according to mice genotype and II) displays  deformations of the reference graph $S_0$ along each PC.}
  \label{fig:exp1}
\end{figure*}

### 2024-09-03 NEURIPS24/paper.tex
Revert "Delete NEURIPS24 directory"
This reverts commit e09ecaea218c43964bb3eb1e2a9a2c5bfd236ded.

 All these state-of-the-art methods previously mentionned \cite{glaunes2008large,oh2024stable,wu2024shape,heo2024logistic} are compared to TS-LDDMM in \Cref{appendix: settings_classification}.
 \vspace{-1ex}
  \section{Limitations and conclusion}
  \vspace{-1ex}
  \label{sec:limitations}

>>>>

 All these state-of-the-art methods previously mentionned \cite{glaunes2008large,oh2024stable,wu2024shape,heo2024logistic} are compared to TS-LDDMM in \Cref{appendix: robustness} and \Cref{appendix: shape_classification}.
 \vspace{-1ex}
  \section{Limitations and conclusion}
  \vspace{-1ex}
  \label{sec:limitations}
